{mscstexta4r}

### 2016-06-16 README.Rmd
Documentation refresh

[Microsoft Cognitive Services](https://www.microsoft.com/cognitive-services/en-us/documentation)
-- formerly known as Project Oxford -- are a set of APIs, SDKs and services
that developers can use to add [AI](https://en.wikipedia.org/wiki/Artificial_intelligence)
features to their apps. Those features include emotion and video detection;
facial, speech and vision recognition; and speech and natural language
processing ([NLP](https://en.wikipedia.org/wiki/Natural_language_processing)).

@@

Per Microsoft's website, the [Text Analytics REST API](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation)
is a suite of text analytics web services built with Azure Machine Learning that
can be used to analyze unstructured text. The API supports the following text
analysis operations:

@@

To use the `{mscstexta4r}` R package, you **MUST** have a valid [account](https://www.microsoft.com/cognitive-services/en-us/pricing)
with Microsoft Cognitive Services. Once you have an account, Microsoft will
provide you with an [API key](https://en.wikipedia.org/wiki/Application_programming_interface_key).
This key will be listed under your subscriptions.

After you've configured `{mscstexta4r}` with your API key, you will be able to
call the Text Analytics REST API from R, up to your maximum number of
transactions per month and per minute.

@@

You can either install the latest **stable** version from CRAN:

@@

Or, you can install the **development** version

@@

@@

>>>>

[Microsoft Cognitive Services](https://www.microsoft.com/cognitive-services/en-us/documentation)
-- formerly known as Project Oxford -- are a set of APIs, SDKs and services
that developers can use to add [AI](https://en.wikipedia.org/wiki/Artificial_intelligence)
features to their apps. Those features include emotion and video detection;
facial, speech and vision recognition; as well as speech and [NLP](https://en.wikipedia.org/wiki/Natural_language_processing).

@@

Per Microsoft's website, the [Text Analytics REST API](https://www.microsoft.com/cognitive-services/en-us/text-analytics/documentation)
is a suite of text analytics web services built with Azure Machine Learning that
can be used to analyze unstructured text. The API supports the following
operations:

@@

@@

To use the `{mscstexta4r}` R package, you **MUST** have a valid [account](https://www.microsoft.com/cognitive-services/en-us/pricing)
with Microsoft Cognitive Services. Once you have an account, Microsoft will
provide you with an [API key](https://en.wikipedia.org/wiki/Application_programming_interface_key)
listed under your subscriptions. After you've configured `{mscstexta4r}` with
your API key, you will be able to call the Text Analytics REST API from R, up
to your maximum number of transactions per month and per minute.

You can install the latest **stable** version of `{mscstexta4r}` from CRAN as
follows:

@@

You can also install the **development** version using `{devtools}`:

@@

```{r eval = FALSE}
# Load yelpChReviews100 text reviews
load("./tests/testthat/data/yelpChineseRestaurantReviews100.rda")

@@

})
# Same results as in synchronous mode
```
